### 2022-07-31 paper/akweury/document.tex
update eval

\section{Evaluation}
We evaluate the trained models on ``synthetic-50-5". 5 objects are considered in the test dataset. They are: $ Baoshanlu $, $ Bus $, $ Dragon $, $ Garfield $, and $ Washington $. Each object has 20 scenes with total 100 scenes for 5 objects. The test objects do not exist in the training dataset. We evaluate all the presented models on the test dataset, in order to fit them in one table, the name of each models are simplified. $ SVD $ model use SVD optimization method, $ NOC $ model is the no skip connection version of $ GCNN $, $ CNN $ is the CNN version of $ GCNN $. $ F1 $, $ F2 $, $ F3 $,$ F4 $ means the fusion times in the Trip-Net.

@@

@@

%% gcnn-eval
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-CNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-NOC.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_SVD.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-CNN.png}
		\caption{CNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-NOC.png}
		\caption{NOC}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_SVD.png}
		\caption{SVD}
	\end{subfigure}

@@

For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net introduced in \ref{sec:trip-net}. 
The qualitative evaluation is shown in figure \ref{fig:trip-eval}. As a comparison, we placed GCNN result in the last column. The training settings for all the models are exact the same to ensure fairness. As shown in the figure, TripNet uses illuminated calibrated RGBD image has a better performance than GCNN model. The dragon scales are sharper in TripNet result. Figure \ref{fig:tripnet-eval-synthetic-zoom-in} gives a closer visualization.
%% TripNet-eval
\begin{figure}[H]
	\centering
		\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
		\caption{Image}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
		\caption{Predict}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_an2-8-1000.png}
	\caption{Error}
\end{subfigure}

@@

	\caption{Normal inference based on Trip-Net. Test image resolution $ 128\times128 $}
	\label{fig:trip-eval}
\end{figure}

%% tripNet zoom in eval
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GT.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_normal_GCNN-GCNN.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_an2-8-1000.png}
	\caption{Trip-Net}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_7_error_GCNN-GCNN.png}
		\caption{GCNN}
	\end{subfigure}

	\caption{Zoom in of the center region of Dragon object. The first row is surface normal, the second row is the corresponding errors.}
	\label{fig:tripnet-eval-synthetic-zoom-in}
\end{figure}

\begin{table}[th]

	\centering
	\begin{tabular}{l l l l l l l }
		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df} & \tabhead{l/i. Nr.}\\
		SVD  & 41.14  & 320.40 & - & - & - & 0 \\ 
		\hline
		GCNN  & 10.64 & 10.44 & 8 & 8,1000 & 0.5 & 0 \\
		\hline
		TripNet-CNN & 10.46 & 28.74 & 8 & 8,1000  & 0.5 & 1 \\
		\hline
		TripNet-F1B & 9.22 &44.59 & 8 & 8,1000  & 0.5 & 1 \\
		\hline
		TripNet & \textbf{9.17} & 43.79 & 8 & 8,1000  & 0.5 & 1 \\
	\end{tabular}
	\caption{A quantitative evaluation on proposed approaches. The angle error is the average angle error of all valid pixels in the test case. The time unit is in millisecond. bz is the batch size, lr-schedule is learning rate schedule. lr-df is learning rate decay factor, l/i. Nr is the number of light-image maps used for each scene}	
	\label{tab:model-error}
\end{table}

\subsection{Comparison}

\newpage
%% Final-Visual
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_SVD.png}
	\end{subfigure}

@@

%% Final-Visual-Zoom-In
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_SVD.png}
	\end{subfigure}

@@

	\caption{Zoom in of the center region of the objects in Figure \ref{fig:final-eval}}
	\label{fig:tripnet-eval-synthetic-zoom-in}
\end{figure}

From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension. It separates the interval $ \left[ -1,1 \right] $, which is exactly the range of normal vector, to 256 sections. Then it counts the number of points locates in each section for 3 axes.  The 3 axes are fitted quite well in most of interval but other than $ \left[ -0.25,0.25 \right] $ for x and y axes and  interval close to $ -1 $ for z axis. Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.

It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?

\subsection{Light Inpainting}
The light inpainting task in this section in order to evaluate the noise inpainting performance of GCNN model. It takes semi-dense light map as input to predict the fully dense light map, as shown in Figure \ref{fig:light-net-archi}. 
The network is trained on 3000 light maps in the "synthetic-50-5" dataset with initial learning rate 0.001, learning schedule 8,1000 with decay factor 0.5, the batch size is 8, the feature map channel is 128 in all of the gated convolution layers. All the models are tested on a laptop with a single NVIDIA GeForce 940MX, 2GB memory.

%% light eval model structure
\begin{figure}[th]
	\centering
	%% https://tex.stackexchange.com/questions/12020/what-is-the-easiest-way-to-draw-a-3d-cube-with-tikz
	\begin{tikzpicture}
		%% -------------------------------------- parameters ------------------------------------------------
		\pgfmathsetmacro{\vdist}{0.4}

		\pgfmathsetmacro{\boxsizea}{2}	%% width 512
		\pgfmathsetmacro{\boxwidtha}{2}	%% width 3

		%% https://www.tug.org/pracjourn/2007-4/walden/color.pdf
		\definecolor{netcolor}{rgb}{0.5,0.7,0.7}

		%% 	d_in							3x512x512
		%%	dconv1: 	d_in-->x1 			32x512x512
		\pgfmathsetmacro{\disttimes}{1}	%% width 32
		\pgfmathsetmacro{\yshift}{1}	%% width 32
		\pgfmathsetmacro{\boxsize}{\boxsizea}	%% size 512
		\pgfmathsetmacro{\boxwidth}{\boxwidtha}	%% width 32
		\pgfmathsetmacro{\yschift}{-1}

		\node[inner sep=0pt] (input) at (\vdist*\disttimes-6,\yschift-0.8)
		{\includegraphics[width=.2\textwidth]{./Figures/gcnn-synthetic/intrinsic_image_light_input.png}};
		\node[text width=3.5cm] at (\vdist*\disttimes-6,\yschift-2.4) {Semi-dense Light Map};

		\node[inner sep=0pt] (output) at (\vdist*\disttimes+3,\yschift-0.8)
		{\includegraphics[width=.2\textwidth]{./Figures/gcnn-synthetic/intrinsic_image_light.png}};
		\node[text width=3.5cm] at (\vdist*\disttimes+3,\yschift-2.4) {fully-dense Light Map};

		\draw [-stealth] (\vdist*\disttimes-4.5,\yschift-1) -- (\vdist*\disttimes-3.5,\yschift-1);
		\draw [-stealth] (\vdist*\disttimes,\yschift-1) -- (\vdist*\disttimes+1,\yschift-1);

		\pgfmathsetmacro{\disttimes}{-2}	%% width 32		
		\pgfmathsetmacro{\yschift}{-1}
		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,-\boxsize,0) -- ++(\boxwidth,0,0) -- cycle;
		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(0,0,-\boxsize) -- ++(0,-\boxsize,0) -- ++(0,0,\boxsize) -- cycle;
		\draw[black, fill=netcolor] (\vdist*\disttimes,\yschift,0) -- ++(-\boxwidth,0,0) -- ++(0,0,-\boxsize) -- ++(\boxwidth,0,0) -- cycle;

		\node[text width=3.5cm] at (\vdist*\disttimes+0.3,\yschift-1) {GCNN};
	\end{tikzpicture}
	\caption{Light map inpainting based on GCNN architecture.}
	\label{fig:light-net-archi}
\end{figure}

The result is shown in Table \ref{tab:light-inpainting}. Besides the GCNN model, we use two extra model as the comparisons. The first one is GCNN-NOC, where NOC means "no skip connection", the second one is CNN, which has the same architecture as the GCNN but only use standard convolution layers in the network.
The GCNN architecture achieves the average angle error lower than 1 degree. As a comparison, U-CNN model has 4 degrees error, which shows the relative weakness of noise filter competence. Besides, the skip connection also booster the performance, since the no skip connection version still has error greater than 1 degree. The both two models for the inpainting task reveals the superiority of GCNN architecture. Figure \ref{fig:light-scatter} and \ref{fig:light-eval} gives a quantitative and qualitative evaluation.

%% light eval table
\begin{table}[H]

	\centering
	\begin{tabular}{l l l l l l }
		\tabhead{Model} & \tabhead{Angle} & \tabhead{Time /ms} & \tabhead{bz} & \tabhead{lr-schedule} & \tabhead{lr-df}\\
		U-GCNN  & 0.59  & 14.45 & 8 & 8,1000 & 0.5\\ 
		\hline
		U-GCNN-NOC & 1.31 & 16.14 & 8 & 8,1000 & 0.5\\
		\hline
		U-CNN & 4.10 & 10.52 & 8 & 8,1000 & 0.5\\
	\end{tabular}
	\caption{The performance of the GCNN model for light map inpainting. The angle error is the average angle error of all valid pixels in the test case. bz stands for batch size, lr-schedule stands for learning rate schedule, lr-df stands for learning rate decay factor.}	
	\label{tab:light-inpainting}
\end{table}

%% light eval visualization
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
		\caption{gray-scale image}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_input.png}
		\caption{Light Direction}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_gt.png}
		\caption{ground-truth}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_light-gcnn.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_light-cnn.png}
		\caption{U-CNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_light-noc.png}
		\caption{U-GCNN-NOC}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_error_light-gcnn.png}
		\caption{U-GCNN Error}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_error_light-cnn.png}
		\caption{U-CNN Error}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_light_error_light-noc.png}
		\caption{U-NOC Error}
	\end{subfigure}

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (10,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_hot-vertical.jpg}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}

	\caption{GCNN Normal Inference for light map inpainting based on dragon object. The degree error map is shown in last row. The average error is shown in the upper right corner in the error map.}
	\label{fig:light-eval}
\end{figure}

%% light eval scatter
\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{./Figures/gcnn-light/scatter-light.png}
	\caption{GCNN for light map inpainting on 100 scenes. The evaluated models are corresponding to the table \ref{tab:light-inpainting}, the line in the figure is the corresponding regression line of each model.}
	\label{fig:light-scatter}
\end{figure}

The evaluation visualization on real dataset is shown in Figure \ref{fig:gcnn-eval-real}
%% fig:gcnn-eval-real
\begin{figure}[th]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_point_cloud_noise.png}
		\caption{point cloud}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_groundtruth.png}
		\caption{ground-truth}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-real/fancy_eval_1_error_GCNN.png}
		\caption{Angle Error}
	\end{subfigure}
	\caption{Evaluation on Real Dataset}
	\label{fig:gcnn-eval-real}
\end{figure}

We evaluate the U-GCNN model on 100 test images as a quantitative evaluation. The result is shown in Figure \ref{fig:scatter-gcnn}. The GCNN based method has average angle error around 10 degrees, whereas the no skip connection version has error above 12 degrees and the CNN version has error above 15 degrees.

%% scatter_gcnn
\begin{figure}[h!]
	\centering
	\includegraphics[width=.8\textwidth]{./Figures/gcnn-synthetic/gcnn-scatter.png}
	\caption{Evaluation of average angular loss on the whole test dataset with 100 scenes. The x-axis indicates the point number, the y-axis indicates the angles. The lines show in the picture are the regression line of each model.}
	\label{fig:scatter-gcnn}
\end{figure}

>>>>

\section{Evaluation}

@@

We evaluate the trained models on ``synthetic-50-5". 5 objects are considered in the test dataset. They are: $ Baoshanlu $, $ Bus $, $ Dragon $, $ Garfield $, and $ Washington $. Each object has 20 scenes with total 100 scenes for 5 objects. The test objects do not exist in the training dataset. We evaluate all the presented models on the test dataset, in order to fit them in one table, the name of each models are simplified. $ SVD $ model use SVD optimization method, $ NOC $ model is the no skip connection version of $ GCNN $, $ CNN $ is the CNN version of $ GCNN $. $ F1 $, $ F2 $, $ F3 $,$ F4 $ means the fusion times in the Trip-Net.

@@

\section{Visualization evaluation on GCNN model}
A qualitative evaluation on object "dragon" is shown in Figure \ref{fig:gcnn-eval}. As shown in the figure, GCNN model achieved a mean angle error in 9 degrees on this dragon object. The image has an overall good performance on the whole object. A closer evaluation is shown in Figure \ref{fig:gcnn-eval-synthetic-zoom-in}, the normal accuracy especially good on the smooth surface, like the body area. In the same case, NOC model as shown in Figure  \ref{fig:gcnn-eval-multi-model} has a overall worse normal than GCNN model in the smooth area. CNN model keeps the skip connection thus gives a sharper result than NOC model, however, the overall smooth part of the model is still worse than GCNN. Besides, the sharp area like the hindleg, the head of dragon object, CNN model gives a much brighter error map (which lead to a higher angle error).

%% GCNN-eval
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
		\caption{Image}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_GCNN-GCNN.png}
		\caption{Predict}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_GCNN-GCNN.png}
		\caption{Error}
	\end{subfigure}

@@

For the approach using illuminated calibrated RGBD image, the task is undertaken by Trip-Net introduced in \ref{sec:trip-net}. 
The qualitative evaluation is shown in figure \ref{fig:trip-eval}. In order to show the effectiveness of added illuminated information, the training settings for all the models are exact the same. We also use the same input as we did in GCNN evaluation. The error of Trip-Net is 6 degree whereas the GCNN is 9.

As shown in the figure \ref{fig:tripnet-eval-synthetic-zoom-in}, the scale on the dragon body is much easier to detect and close to the ground-truth. The head region gives a sharper edge prediction. All of the five sampled zoom-in regions in the Trip-Net has a better performance than GCNN.

%% TripNet-eval
\begin{figure}[H]
	\centering
		\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_img.png}
		\caption{Image}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_groundtruth.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_normal_an2-8-1000.png}
		\caption{Predict}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_7_error_an2-8-1000.png}
	\caption{Error}
\end{subfigure}

@@

	\caption{Normal inference based on Trip-Net. Test image has resolution $ 128\times128 $}
	\label{fig:trip-eval}
\end{figure}

%% tripNet zoom in eval
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_22_-8_normal.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_2_22_normal.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_normal.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_normal.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_12_-48_normal.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_22_-8_error.png}
		\caption{Scale}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_2_22_error.png}
	\caption{Head}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_32_12_error.png}
	\caption{Foreleg}
\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
	\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_42_-28_error.png}
	\caption{Hindleg}
\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/tripnet_synthetic/eval_7_12_-48_error.png}
		\caption{Tail}
	\end{subfigure}

	\caption{Zoom in of some regions of Dragon object. The first row is surface normal, the second row is the corresponding errors. Zoom-in normal map corresponding $ 32\times32 $ points in the original matrix.}
	\label{fig:tripnet-eval-synthetic-zoom-in}
\end{figure}

\section{More Comparison}
Figure \ref{fig:final-eval} gives more visualization on model SVD, GCNN and Trip-Net. Figure \ref{fig:final-eval-zoom-in} is the corresponding zoom-in visualization.
\newpage
%% Final-Visual
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/visual_eval/fancy_eval_2_normal_SVD.png}
	\end{subfigure}

@@

%% Final-Visual-Zoom-In
\begin{figure}
	\centering
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GT.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_an2-8-1000.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_GCNN-GCNN.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/visual_eval/eval_2_normal_SVD.png}
	\end{subfigure}

@@

	\caption{Zoom in of the center region of the objects in Figure \ref{fig:final-eval}}
	\label{fig:final-eval-zoom-in}
\end{figure}
